Conflict-Free Vertex Coloring Of Planar Graphs

### 2017-04-16 paper/paper.tex
Making minor format changes

The k-colorability problem and the conflict-free k-colorability problem are NP-complete. This can be proven by using a reduction from a known NP-complete problem. If we find a known hard problem $Y$, we can prove that another problem $X$ is hard by a reduction from $Y$ to $X$. The VCP and the CFCP have both been shown to be NP-hard \cite{abel2017three,moret1998theory}. The \emph{k-colorability} problem is proven to be NP-complete with a reduction from 3-SAT, a well-known NP-complete problem \cite{sharma2012new}.

@@

The problem when initially setting up these networks comes into play when assigning frequencies. Imagine two base-stations near each other having the same frequency. If a client is in reception range of both base-stations, then mutual interference occurs and the radio link is too noisy to be used for proper communication. The goal is to assign frequencies to base stations such that every client is served by some base-station and to minimize the number of frequencies used.

@@

\subsection{Iterated Elimination of Distance-3-Sets}
\label{sec:iterated}
The iterated elimination of distance-3-sets algorithm, given in \cite{abel2017three}, is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in Theorem \ref{thm:criterion}. If the criterion is not met, the heuristic will not generate a valid conflict-free coloring of $k$ colors.

>>>>

The k-colorability problem as well as the conflict-free k-colorability problem are NP-complete. This can be proven by using a reduction from a known NP-complete problem. If we find a known hard problem $Y$, we can prove that another problem $X$ is hard by a reduction from $Y$ to $X$. The VCP and the CFCP have both been shown to be NP-hard \cite{abel2017three,moret1998theory}. The \emph{k-colorability} problem is proven to be NP-complete with a reduction from 3-SAT, a well-known NP-complete problem \cite{sharma2012new}.

@@

The main problem when initially setting up these networks comes into play when assigning frequencies. Imagine two base-stations near each other having the same frequency. If a client is in reception range of both base-stations, then mutual interference occurs and the radio link is too noisy to be used for proper communication. The goal is to assign frequencies to base stations such that every client is served by some base-station and to minimize the number of frequencies used.

@@

\vspace{-0.5cm}

\subsection{Iterated Elimination of Distance-3-Sets}
\label{sec:iterated}
The iterated elimination of distance-3-sets algorithm, defined in \cite{abel2017three}, is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in Theorem \ref{thm:criterion}. If the criterion is not met, the heuristic will not generate a valid conflict-free coloring of $k$ colors.
